Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-11-12 main.Rmd
structure cleaned

# Proposed measure: Median Maximum Pairwise Distances (MMPD)

@@

@@

# Computation

## Distance between distributions

@@

### Distribution of Jensen-Shannon distances

@@

## Simulation study

@@

### Design and analysis of simulation experiments

The behavior of the test statistic is monitored and understood through simulation experiments. A single simulation consisting of computational operations on a panel generating MMPD the value of which represents to what extent a pair of cyclic granularities would be interesting when displayed in the design. In comparing different simulation runs, we distinguish between different distributions and simulation scenarios (also iterations may be).

#### Simulated designs:

@@

#### Environment

@@

#### Experimental set up

@@

#### Simulation results

##### Null distribution

@@

Algorithm for computation for all harmony pairs

@@

@@

# Visualisation

Leader plots like in Scagnostics paper

@@

>>>>

# Median Maximum Pairwise Distances (MMPD)

@@

## Idea

@@

## Computation

### Distance between distributions

@@

#### Distribution of Jensen-Shannon distances

@@

## Performance

# Simulation study

@@

<!-- ### Design and analysis of simulation experiments -->

The behavior of the measure is monitored and understood through simulation experiments. A single simulation consisting of computational operations on a panel generating MMPD the value of which represents to what extent a pair of cyclic granularities would be interesting when displayed in the design. In comparing different simulation runs, we distinguish between different distributions and simulation scenarios (also iterations may be).

## Simulated designs

@@

## Environment

@@

## Experimental set up

@@

## Results

### Null distribution

Objective: distribution equal and hence values could be compared and normalisation works

@@

## Algorithm

for computation for all harmony pairs

@@

## Size, power and confidence interval

@@

@@

# Appendix

<!-- # Visualisation -->

<!-- Leader plots like in Scagnostics paper -->
